Applicability of SSM and UML for Designing a Search Application for the British Broadcasting Corporation (BBC)

### 2014-11-02 academy-talk.tex
Added talk to be given at the Academy course.

\usetheme{Frankfurt}
\usecolortheme{seagull}

@@

\title{Applicability of SSM and UML for Designing a Search Application for the British Broadcasting Corporation (BBC)}
\author{Ross Fenning\inst{1}
  \and Huseyin Dogan\inst{2}
  \and Keith Phalp\inst{2}}
\institute{BBC, UK \\ \email{Ross.Fenning@bbc.co.uk}
  \and Bournemouth University, UK \\ \email{\{hdogan,kphalp\}@bournemouth.ac.uk}}
\date{2014-06-17}

@@

% Background
\begin{frame}
  \frametitle{About Me}
  \begin{itemize}
    \pause \item Senior Software Engineer
    \pause \item BBC Future Media
    \pause \item Content Discovery: Search
    \pause \item BBC Academy and University of Bradford, UK
    \pause \item Bournemouth University and Lancaster University
    \pause \item School of Design Engineering \& Computing at Bournemouth University
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{BBC Search results}
  \includegraphics[width=\linewidth]{results.png}
\end{frame}

\begin{frame}
  \frametitle{BBC iPlayer Search results}
  \includegraphics[width=\linewidth]{iplayer.png}
\end{frame}

\begin{frame}
  \frametitle{CBBC Search results}
  \includegraphics[width=\linewidth]{cbbc.png}
\end{frame}

\begin{frame}
  \frametitle{Why BBC Search?}
  \framesubtitle{Isn't Google good enough?}
  \begin{itemize}
    \pause \item We can search the BBC via Google
    \pause \item What can the BBC offer that Google cannot?
    \pause \item Domain knowledge about our own content
    \pause \item More ``real time'' updates of content
  \end{itemize}
\end{frame}

>>>>

\usetheme{Copenhagen}
\usecolortheme{default}

@@

\title{Applicability of SSM and UML for Designing a Search Application for the British Broadcasting Corporation (BBC)}
\author{Ross Fenning\inst{1}
  \and Huseyin Dogan\inst{2}
  \and Keith Phalp\inst{2}}
\institute{BBC, UK \\ \email{Ross.Fenning@bbc.co.uk}
  \and Bournemouth University, UK \\ \email{\{hdogan,kphalp\}@bournemouth.ac.uk}}
\date{2014-11-05}

@@

% Background
\begin{frame}
  \frametitle{About Me}
  \begin{itemize}
    \pause \item Senior Software Engineer
    \pause \item Future Media: Content Discovery: Search
  \end{itemize}
\end{frame}

@@
